---
title: "CREDIT RISK"
author: "NIKHIL AIVALLI"
date: "December 12, 2017"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```
#Read data
```{r}
CR <- read.csv('D:/IMARTICUS/R/dataset/R_Module_Day_7.2_Credit_Risk_Train_data.csv',na.strings = c(""," ","NA"))
#View(CR)
attach(CR)
```
#EDA
#EDA:Remove irrelevant variables
```{r}
CR$Loan_ID=NULL

#Identify missing values using colSums 
summary(CR)
sum(is.na(CR))
colSums(is.na(CR))
```
#imputation
#Replace it with mean/median/mode

```{r}
acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}

mode <- function(y){
  uniq<- unique(y)
  uniq[which.max(tabulate(match(y,uniq)))]
}

CR$Gender[is.na(CR$Gender)]<- mode(CR$Gender)
CR$Married[is.na(CR$Married)]<-mode( CR$Married)
CR$Dependents[is.na(CR$Dependents)]<- mode(CR$Dependents)
CR$Self_Employed[is.na(CR$Self_Employed)]<- mode(CR$Self_Employed)
CR$LoanAmount[is.na(CR$LoanAmount)]<- median(CR$LoanAmount,na.rm = T)
CR$Loan_Amount_Term[is.na(CR$Loan_Amount_Term)]<- median(CR$Loan_Amount_Term,na.rm = T)
CR$Credit_History[is.na(CR$Credit_History)]<- mode(CR$Credit_History)

#covert CR$Credit_History to factor
CR$Credit_History<-as.factor(CR$Credit_History)
class(CR$Credit_History)

```
#Classification using decision tree
```{r message=TRUE}

library(rpart)
model_CR_DL = rpart(Loan_Status~.,data=CR) # classification

```
#classification using Logistic Regression
```{r}
model_CR_LR<- glm(Loan_Status~Married+Credit_History+Property_Area,family = binomial(link = 'logit'),data=CR)
summary(model_CR_LR)
```
#classification using SVM
```{r warning=FALSE}
library(e1071)
model_CR_SVM<- svm(formula=Loan_Status~.,data=CR,type='C-classification',kernel='linear')
summary(model_CR_SVM)
```
#CLASSIFICATION USING NAIVE BAYES
```{r}
#library(e1071)
model_CR_NB<-naiveBayes(Loan_Status~.,data=CR)
```

#classification using random forest
```{r}
library(randomForest)
model_CR_RF<-randomForest(x=CR[,-12],
                      y=CR[,12],
                      ntree = 500)
```

#VALIDATION DATASET ,reading imputing

```{r}
cr_v <- read.csv('D:/IMARTICUS/R/dataset/R_Module_Day_8.2_Credit_Risk_Validate_data.csv',na.strings = c(""," ","NA"))
#check for data issues with testa nd clean it for the same
colSums(is.na(cr_v))
#cr_v$Loan_Status<-ifelse(cr_v$Loan_Status=="Y",1,0)
cr_v$LoanAmount[is.na(cr_v$LoanAmount)] <- mean(cr_v$LoanAmount,na.rm=T)
cr_v$Loan_Amount_Term[is.na(cr_v$Loan_Amount_Term)] <- mean(cr_v$Loan_Amount_Term,na.rm=T)
cr_v$Credit_History[is.na(cr_v$Credit_History)]<-mode(cr_v$Credit_History)
cr_v$Self_Employed[is.na(cr_v$Self_Employed)]<-mode(cr_v$Self_Employed)
cr_v$Dependents[is.na(cr_v$Dependents)]<-mode(cr_v$Dependents)
cr_v$Gender[is.na(cr_v$Gender)]<-mode(cr_v$Gender)
cr_v$Married[is.na(cr_v$Married)]<-mode( cr_v$Married)

cr_v$Loan_ID=NULL
cr_v$Credit_History<-as.factor(cr_v$Credit_History)
```
#CLAssification & validation using KNN
```{r}
library(class)
#cr_v$Loan_Status<- ifelse(cr_v$Loan_Status=="Y",1,0)
#CR$Loan_Status<- ifelse(CR$Loan_Status=="Y",1,0)
CR$Loan_Status<- as.factor(CR$Loan_Status)
cr_v$Loan_Status<-as.factor(cr_v$Loan_Status)

#CR1<- CR[,-c(1,2,3,4,5,11,10)]
#CR2<- cr_v[,-c(1,2,3,4,5,11,10)]
CR_K<-CR
cr_v_k<-cr_v

levels(CR_K$Gender)<-1:2
levels(CR_K$Married)<-1:2
levels(CR_K$Dependents)<-1:4
levels(CR_K$Education)<-1:2
levels(CR_K$Self_Employed)<-1:2
levels(CR_K$Property_Area)<-1:3

CR_K$Gender<-as.numeric(CR_K$Gender)
CR_K$Married<-as.numeric(CR_K$Married)
CR_K$Dependents<-as.numeric(CR_K$Dependents)
CR_K$Education<-as.numeric(CR_K$Education)
CR_K$Self_Employed<-as.numeric(CR_K$Self_Employed)
CR_K$Property_Area<-as.numeric(CR_K$Property_Area)
CR_K$Credit_History<-as.numeric(CR_K$Credit_History)

levels(cr_v_k$Gender)<-1:2
levels(cr_v_k$Married)<-1:2
levels(cr_v_k$Dependents)<-1:4
levels(cr_v_k$Education)<-1:2
levels(cr_v_k$Self_Employed)<-1:2
levels(cr_v_k$Property_Area)<-1:3

cr_v_k$Gender<-as.numeric(cr_v_k$Gender)
cr_v_k$Married<-as.numeric(cr_v_k$Married)
cr_v_k$Dependents<-as.numeric(cr_v_k$Dependents)
cr_v_k$Education<-as.numeric(cr_v_k$Education)
cr_v_k$Self_Employed<-as.numeric(cr_v_k$Self_Employed)
cr_v_k$Property_Area<-as.numeric(cr_v_k$Property_Area)
cr_v_k$Credit_History<-as.numeric(cr_v_k$Credit_History)



model_CR_KNN=knn(train =CR_K[,-12] ,
              test = cr_v_k[,-12],
              cl=CR_K[,12],
              k=20,prob = TRUE)
model_CR_KNN<-as.numeric(model_CR_KNN)

#model_CR_KNN<-ifelse(model_CR_KNN>0.5,1,0)
#View(CR2)
CF_CR_KNN<- table(model_CR_KNN,cr_v_k$Loan_Status)
CF_CR_KNN

acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(CF_CR_KNN)
library(ROCR)

pr_CR_KNN<- prediction(model_CR_KNN,cr_v_k$Loan_Status)
#length(cr_v$Loan_Status)
prf_CR_KNN<- performance(pr_CR_KNN,measure = "tpr",x.measure = "fpr")
plot(prf_CR_KNN)

#obtaining area under ROC curve
auc_CR_KNN<-performance(pr_CR_KNN,measure = "auc")
auc_CR_KNN<- auc_CR_KNN@y.values[[1]]
auc_CR_KNN
```
#validating using decision tree
```{r}
validate_CR_DL <- predict(model_CR_DL,newdata=cr_v,type='class')
validate_CR_DL <- ifelse(validate_CR_DL =="Y",1,0)


#Confusion matrix
cf_CR_DL<-table(validate_CR_DL,cr_v$Loan_Status)
cf_CR_DL
#function for accuracy
acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(cf_CR_DL)

library(ROCR)


pr_CR_DL<- prediction(validate_CR_DL,cr_v$Loan_Status)
#length(cr_v$Loan_Status)
prf_CR_DL<- performance(pr_CR_DL,measure = "tpr",x.measure = "fpr")
plot(prf_CR_DL)

#obtaining area under ROC curve
auc_CR_DL<-performance(pr_CR_DL,measure = "auc")
auc_CR_DL<- auc_CR_DL@y.values[[1]]
auc_CR_DL

#prediction for the prediction set
plot(model_CR_DL,uniform=TRUE,cex=0.8)
text(model_CR_DL, use.n=TRUE, all=TRUE)

```





#validating using logistic regression
```{r}
#validation of our model using validation set
validate_CR_LR <- predict(model_CR_LR,newdata=cr_v,type='response')
validate_CR_LR <- ifelse(validate_CR_LR >=0.5,1,0)

#Confusion matrix
cf_CR_LR<-table(validate_CR_LR,cr_v$Loan_Status)
cf_CR_LR
#function for accuracy
acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(cf_CR_LR)

library(ROCR)

pr_CR_LR<- prediction(validate_CR_LR,cr_v$Loan_Status)
#length(cr_v$Loan_Status)
prf_CR_LR<- performance(pr_CR_LR,measure = "tpr",x.measure = "fpr")
plot(prf_CR_LR)

#obtaining area under ROC curve
auc_CR_LR<-performance(pr_CR_LR,measure = "auc")
auc_CR_LR<- auc_CR_LR@y.values[[1]]
auc_CR_LR
#help(ROCR)
```
#validating using SVM
```{r}
#predicting 
validate_CR_SVM<-predict(model_CR_SVM,cr_v)
validate_CR_SVM<-ifelse(validate_CR_SVM=="Y",1,0)
#confusion matrix
cf_CR_SVM<-table(validate_CR_SVM,cr_v$Loan_Status)
cf_CR_SVM

#function for accuracy
acc<-function(cfSVM){
  Totp<-cfSVM[2,1]+cfSVM[2,2]
  TP<-cfSVM[2,2]
  c<-TP/Totp
  c
}
acc(cf_CR_SVM)

library(ROCR)
pr_CR_SVM<- prediction(validate_CR_SVM,cr_v$Loan_Status)
#length(cr_v$Loan_Status)
prf_CR_SVM<- performance(pr_CR_SVM,measure = "tpr",x.measure = "fpr")
plot(prf_CR_SVM)

#obtaining area under ROC curve
auc_CR_SVM<-performance(pr_CR_SVM,measure = "auc")
auc_CR_SVM<- auc_CR_SVM@y.values[[1]]
auc_CR_SVM
#help(ROCR)

```
#VALIDATING USING NAIVE BAYES
```{r}
#predicting 
validate_CR_NB<-predict(model_CR_NB,cr_v)
validate_CR_NB<-ifelse(validate_CR_NB=="Y",1,0)
#confusion matrix
cf_CR_NB<-table(validate_CR_NB,cr_v$Loan_Status)
cf_CR_NB

#function for accuracy
acc<-function(cfSVM){
  Totp<-cfSVM[2,1]+cfSVM[2,2]
  TP<-cfSVM[2,2]
  c<-TP/Totp
  c
}
acc(cf_CR_NB)

library(ROCR)
pr_CR_NB<- prediction(validate_CR_NB,cr_v$Loan_Status)
#length(cr_v$Loan_Status)
prf_CR_NB<- performance(pr_CR_NB,measure = "tpr",x.measure = "fpr")
plot(prf_CR_NB)

#obtaining area under ROC curve
auc_CR_NB<-performance(pr_CR_NB,measure = "auc")
auc_CR_NB<- auc_CR_NB@y.values[[1]]
auc_CR_NB
```
#VALIDATING USING RANDOM FOREST
```{r}
validate_CR_RF<- predict(model_CR_RF,newdata =cr_v)
validate_CR_RF<-as.numeric(validate_CR_RF)
CF_RF<-table(validate_CR_RF,cr_v$Loan_Status)
CF_RF
acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(CF_RF)

library(ROCR)

pr_CR_RF<- prediction(validate_CR_RF,cr_v$Loan_Status)
#length(cr_v$Loan_Status)
prf_CR_RF<- performance(pr_CR_RF,measure = "tpr",x.measure = "fpr")
plot(prf_CR_RF)

#obtaining area under ROC curve
auc_CR_RF<-performance(pr_CR_RF,measure = "auc")
auc_CR_RF<- auc_CR_RF@y.values[[1]]
auc_CR_RF
```
#TESTING
```{r}
#cr_test1 <- read.csv('D:/IMARTICUS/R/dataset/R_Module_Day_8.1_Credit_Risk_Test_data.csv',na.strings = c(""," ","NA"))

#cr_test1$Credit_History<-as.factor(cr_test1$Credit_History)

#fr_p1<- predict(classifier,newdata = cr_test1,type ='class')
#fr_p <- ifelse(fitted.results1 >=0.5,1,0)


#cr_test1<-data.frame(cr_test1,fr_p1)

#View(cr_test1)

```