---
title: "Network_Intrusion_classification"
author: "NIKHIL AIVALLI"
date: "December 11, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Read data
```{r}
dataset=read.csv('D:/IMARTICUS/R/Business case_Network intrusion_R/Network_Intrusion_Train_data.csv',na.strings = c(""," ","NA"))
attach(dataset)
#View(dataset)
```
#EDA
#EDA:Remove irrelevant variables
```{r}
dataset$num_outbound_cmds =NULL
dataset$is_host_login=NULL
summary(dataset)
colSums(is.na(dataset))

dataset$class<- factor(dataset$class)

#Convert nominal variables to numeric codes such as flag, protocol type, service
levels(dataset$service)<-1:70
levels(dataset$flag)<-1:11
levels(dataset$protocol_type)<-1:3
summary(dataset)

#hist(duration)

normalise <- function(x, na.rm = TRUE) {
  ranx <- range(x, na.rm = na.rm)
  (x - ranx[1]) / diff(ranx)
}
apply(dataset[,c(1,5,6,10,13,16,17,21,22,30,31)],2,normalise)
#or
#scale(dataset[,c(1,5,6,10,13,16,17,21,22,30,31)])
```
#Classification using decision tree
```{r}
library(rpart)
modelDT = rpart(formula = class ~ .,data = dataset)
```
#classification using Logistic Regression
```{r}
modelLR1<-glm(class~.,family = binomial(link = 'logit'),data=dataset)
summary(modelLR1)

modelLR2<- glm(class~duration+service+flag+src_bytes+dst_bytes+land+hot+
                 num_failed_logins+logged_in +num_compromised+num_root+
                 is_guest_login+count+srv_count+serror_rate +srv_serror_rate
               +rerror_rate+srv_rerror_rate+same_srv_rate+diff_srv_rate                         +srv_diff_host_rate+dst_host_count+dst_host_srv_count
               +dst_host_same_srv_rate+
                dst_host_diff_srv_rate +dst_host_same_src_port_rate+
                 dst_host_srv_diff_host_rate+dst_host_srv_serror_rate+
                 dst_host_rerror_rate,
               family = binomial(link = 'logit'),data=dataset)
               
            
summary(modelLR2)
modelLR3<- glm(class~duration+service+flag+src_bytes+dst_bytes+land+hot+
                 num_failed_logins+logged_in +num_compromised+num_root+
                 is_guest_login+count+srv_count+serror_rate +srv_serror_rate
               +rerror_rate+srv_rerror_rate+same_srv_rate+diff_srv_rate                         +srv_diff_host_rate+dst_host_count+dst_host_srv_count
               +dst_host_same_srv_rate+
              dst_host_same_src_port_rate+
                 dst_host_srv_diff_host_rate+dst_host_srv_serror_rate+
                 dst_host_rerror_rate,
               family = binomial(link = 'logit'),data=dataset)


summary(modelLR3)
```
#classification using SVM
```{r}
library(e1071)
model_svm_L<-svm(formula=class~.,
                 data=dataset,
                 type='C-classification',
                 kernel='linear')

model_svm_R<-svm(formula=class~.,
                 data=dataset,
                 type='C-classification',
                 kernel='radial')

model_svm_S<-svm(formula=class~.,
                 data=dataset,
                 type='C-classification',
                 kernel='sigmoid')

model_svm_P<-svm(formula=class~.,
                 data=dataset,
                 type='C-classification',
                 kernel='polynomial')


detach(dataset)
```
#calssification using Naive Bayes
```{r}
#library(e1071)
model_NB<-naiveBayes(class~.,data = dataset)
```
#CLAssification & validation using KNN
```{r}
library(class)
model_KNN=knn(train = dataset[,-40],
              test = dataset_V[,-40],
              cl=dataset[,40],
              k=200,prob = TRUE)
model_KNN<-ifelse(model_KNN=="normal",1,0)
#View(dataset)

CF_KNN<- table(model_KNN,dataset_V$class)
CF_KNN

acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(CF_KNN)

pr_KNN<- prediction(model_KNN,dataset_V$class)
#length(cr_v$Loan_Status)
prf_KNN<- performance(pr_KNN,measure = "tpr",x.measure = "fpr")
plot(prf_KNN)

#obtaining area under ROC curve
auc_KNN<-performance(pr_KNN,measure = "auc")
auc_KNN<- auc_KNN@y.values[[1]]
auc_KNN
```
#CLASSIFICATION USING RANDOM FOREST
```{r}
model_RF<-model_RF<-randomForest(x=dataset[,-40],
                      y=dataset[,40],
                      ntree = 500)
```
#VALIDATION DATASET ,reading imputing
```{r}
dataset_V=read.csv('D:/IMARTICUS/R/Business case_Network intrusion_R/Network_Intrusion_Validate_data.csv',na.strings = c(""," ","NA"))
#attach(dataset_V)
View(dataset_V)

dataset_V$num_outbound_cmds =NULL
dataset_V$is_host_login=NULL
summary(dataset_V)
colSums(is.na(dataset_V))

dataset_V$class<- factor(dataset_V$class)

#Convert nominal variables to numeric codes such as flag, protocol type, service
levels(dataset_V$service)<-1:70
levels(dataset_V$flag)<-1:11
levels(dataset_V$protocol_type)<-1:3
summary(dataset_V)

apply(dataset_V[,c(1,5,6,10,13,16,17,21,22,30,31)],2,normalise)
```
#VALIDATION USING DECISION TREE
```{r}
validate_DT <- predict(modelDT,newdata=dataset_V,type='class')
validate_DT <- ifelse(validate_DT=="normal",1,0)


#Confusion matrix
cf_DT<-table(validate_DT,dataset_V$class)
cf_DT
#function for accuracy
acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(cf_DT)

library(ROCR)

pr_DT<- prediction(validate_DT,dataset_V$class)
#length(cr_v$Loan_Status)
prf_DT<- performance(pr_DT,measure = "tpr",x.measure = "fpr")
plot(prf_DT)

#obtaining area under ROC curve
auc_DT<-performance(pr_DT,measure = "auc")
auc_DT<- auc_DT@y.values[[1]]
auc_DT

#prediction for the prediction set
#plot(modelDT,uniform=TRUE,cex=0.8)
#text(modelDT, use.n=TRUE, all=TRUE)
```
#VALIDATION USING logistic regression
```{r}
#validation of our model using validation set
validate_LR <- predict(modelLR3,newdata=dataset_V,type='response')
validate_LR <- ifelse(validate_LR >0.5,1,0)

#Confusion matrix
cf_LR<-table(validate_LR,dataset_V$class)
cf_LR
#function for accuracy
acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(cf_LR)

library(ROCR)

pr_LR<- prediction(validate_LR,dataset_V$class)
#length(cr_v$Loan_Status)
prf_LR<- performance(pr_LR,measure = "tpr",x.measure = "fpr")
plot(prf_LR)

#obtaining area under ROC curve
auc_LR<-performance(pr_LR,measure = "auc")
auc_LR<- auc_LR@y.values[[1]]
auc_LR
#help(ROCR)
```
#VALIDATION USING SVM
```{r}
validate_SVM_L=predict(model_svm_L,newdata = dataset_V)
validate_SVM_L=ifelse(validate_SVM_L=="normal",1,0)

validate_SVM_R=predict(model_svm_R,newdata = dataset_V)
validate_SVM_S=predict(model_svm_S,newdata = dataset_V)
validate_SVM_P=predict(model_svm_P,newdata = dataset_V)

CF_SVM_L=table(validate_SVM_L,dataset_V$class)
CF_SVM_R=table(validate_SVM_R,dataset_V$class)
CF_SVM_S=table(validate_SVM_S,dataset_V$class)
CF_SVM_P=table(validate_SVM_P,dataset_V$class)

acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(CF_SVM_L)
acc(CF_SVM_R)
acc(CF_SVM_S)
acc(CF_SVM_P)

library(ROCR)

pr_SVM_L<- prediction(validate_SVM_L,dataset_V$class)
#length(cr_v$Loan_Status)
prf_SVM_L<- performance(pr_SVM_L,measure = "tpr",x.measure = "fpr")
plot(prf_SVM_L)

#obtaining area under ROC curve
auc_SVM_L<-performance(pr_SVM_L,measure = "auc")
auc_SVM_L<- auc_SVM_L@y.values[[1]]
auc_SVM_L
```
#validation using Naive Bayes
```{r}
Validate_NB<-predict(model_NB,dataset_V)
Validate_NB=ifelse(Validate_NB=="normal",1,0)
CF_NB=table(Validate_NB,dataset_V$class)
CF_NB

acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(CF_NB)

pr_NB<- prediction(Validate_NB,dataset_V$class)
#length(cr_v$Loan_Status)
prf_NB<- performance(pr_NB,measure = "tpr",x.measure = "fpr")
plot(prf_NB)

#obtaining area under ROC curve
auc_NB<-performance(pr_NB,measure = "auc")
auc_NB<- auc_NB@y.values[[1]]
auc_NB

```
#validation using random forest
```{r}
validate_RF<- predict(model_RF,newdata =dataset_V)
#validate_RF<-as.numeric(validate_RF)
CF_RF<-table(validate_RF,dataset_V$class)
CF_RF
acc<-function(cf1){
  Totp<-cf1[2,1]+cf1[2,2]
  TP<-cf1[2,2]
  c<-TP/Totp
  c
}
acc(CF_RF)

library(ROCR)

pr_RF<- prediction(validate_RF,dataset_V$class)
#length(cr_v$Loan_Status)
prf_RF<- performance(pr_RF,measure = "tpr",x.measure = "fpr")
plot(prf_RF)

#obtaining area under ROC curve
auc_RF<-performance(pr_RF,measure = "auc")
auc_RF<- auc_RF@y.values[[1]]
auc_RF

```