---
title: "EDA Assignment-2"
author: "NIKHIL AIVALLI"
date: "10 September 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1)	Load the dataset early_senate_polls.csv file.
```{r}
#we load a data set into R using read.csv command
ds=read.csv("D:/EDA/assignment 2/early-senate-polls.csv")
```

2)	Find the number of rows and columns in the dataset
```{r}
#nrow provides the number of rows and ncol gives the number of columns
rows=nrow(ds)
cols=ncol(ds)
cat("Number of rows=",rows,"\n")
cat("number of columns=",cols,"\n")
```

3)	Check the class type of each column
```{r}
#str function provides the type of each column with respective values.
str(ds)
```

4)	Use the dplyr package
```{r}
#require command check if the required package is installed,if not, then it will install and load it.
require(dplyr)
```

5)	For each year, calculate the average of presidential_approval
```{r}
# for this we intially do groupby year and get the mean for the respective years using summarise function.

ds %>% group_by(year) %>% summarise(avg_presidential_approval=mean(presidential_approval,na.rm=TRUE))
```

6)	Show only the rows where the average presidential_approval obtained in the above step is greater than 100.
```{r}
#here the required condition is obtained using filter command by using the new variable created in summarise function.

ds %>% group_by(year) %>% summarise(avg_presidential_approval=mean(presidential_approval,na.rm=TRUE)) %>%  filter(avg_presidential_approval>100)
```

7)	Use the dplyr package to select the 
    a.	columns year and poll_average
    b.	For each year, find the maximum value of poll_average

```{r}
#a.columns year and poll_average
ds%>%select(year,poll_average)

#b.For each year, find the maximum value of poll_average

#to find the maximum value for each year,we first use groupby function and find maximum using summarise function

ds %>%  group_by(year) %>% summarise(max_poll_average=max(poll_average,na.rm=TRUE))
```

8)	select year and election_result and arrange the results in order(ascending) of election_result 

```{r}
#to get the result in ascending order we use arrange function.for descending order we use desc(election_result).

ds %>% select(year,election_result) %>% arrange(election_result)
```

9)	Use the dplyr package to select
   a.	Year and poll_average for each year
   b.	Retrieve the maximum value of poll_average and store it in a new variable max_poll_aver.

```{r}
#a.select Year and poll_average for each year

ds %>% select(year,poll_average) %>% group_by(year)

#For each year, calculate the average of poll_average

ds %>% group_by(year) %>% summarise(avg_poll_average=mean(poll_average,na.rm=TRUE))


#b.Retrieve the maximum value of poll_average and store it in a new variable max_poll_aver.

#we use the summarise function

max_poll_aver= ds %>% summarise(max(poll_average))
max_poll_aver
```


 


